### 2022-06-01 main.tex
some more thoughts

Next, we consider a more realistic scenario in which immunity provides protection against symptoms, $\epsilon_s = 0.4$, and infection, $\epsilon_i = 0.4$ (\fref{variant}D--F).
In this case, cross protection against infection has a disproportionately larger effect on the more severe (orange) variant, causing its peak infection prevalence (\fref{variant}E) and fatality (\fref{variant}F) to be lower than that of the original, wildtype variant.
Across a wide range of asymptomatic proportion $p$, we find that this immunity profile is sufficient to prevent worse outcomes at the population level.

In summary, using a simplified model we have shown that asymptomatic infections can represent a double-edge sword insofar as they represent a better outcome for some individuals but a mechanism for onwards transmission that leads to a worse outcome for the population as a whole.
Extending our framework further shows that the immunity profile plays a critical role in determining the dynamics of future variants:
while protection against symptoms prevent diseases at the individual level, it can inadvertently lead to more infections, and potentially deaths, at the population level.
For example, milder variants can result in even faster epidemic growth rates and larger outbreaks, even though it can lead to less fatalities if the variant is sufficiently mild.

Our simulations of invading variants resemble the dynamics of the SARS-CoV-2 Omicron variant.
Despite moderate levels of vaccine effectiveness against symptomatic and severe cases caused by the Omicron variant, especially after booster shots \citep{andres2022omicron}, both vaccine- and infection-derived immunity has provided limited protection against infections \citep{pearson2021omicron}.
Its immune evasive property allowed the Omicron variant to cause more infections in South Africa than previous variants \citep{sun2022omicron};
therefore, even though the Omicron variant has been estimated to be milder \citep{MENNI20221618,ulloa2022estimates}, the number of hospitalizations and deaths caused by the Omicron variant have remained high \citep{Iacobuccio254,faust2022omicron,sigal2022estimating}.

There are several limitations to our analysis.
First of all, behavioral and intervention effects must sufficiently high in order for the fatality to peak at intermediate levels of asymptomaticity.
While we are able to generalize our results using more realistic models, incorporating both presymptomatic and asymptomatic transmission, the transmission rate needs to be reduced by at least 60\% after symptom onset for us to see the nonlinear effects of subclinical transmission on population-level outcomes.
\swp{what are some other limitations we should address?}

SARS-CoV-2 has proven hard to control in large part because transmission is often decoupled from symptoms. 
Although mitigation efforts have often prioritized responding to symptoms---including symptom-based testing, fever checks, mask-wearing for infectious individuals---a different approach that strives to reduce the chance of asymptomatic transmission while increasing treatment of symptomatically infected individuals could both reduce infection risk at the source and in the event that individuals are at risk for severe outcomes.
As more variants continue to emerge, updating vaccines to prevent infections, and not just diseases, will be critical to controlling the course of the pandemic.

>>>>

Next, we consider a more realistic scenario in which immunity provides protection against both symptoms, $\epsilon_s = 0.4$, and infection, $\epsilon_i = 0.4$ (\fref{variant}D--F).
In this case, cross protection against infection has a large effect on the more severe (orange) variant, causing its peak infection prevalence (\fref{variant}E) and fatality (\fref{variant}F) to be lower than that of the original, wildtype variant.
Across a wide range of asymptomatic proportion $p$, we find that this immunity profile is sufficient to prevent worse outcomes at the population level.

In summary, using a simplified model we have shown that asymptomatic infections can represent a double-edged sword by providing a better outcome for some individuals while facilitating onward transmission that leads to a worse outcome for the population as a whole.
Extending our framework further shows that the immunity profile plays a critical role in determining the dynamics of future variants:
while protection against symptoms protects health at the individual level, it can lead to more infections, and potentially more deaths, at the population level.

Our simulations of invading variants resemble the dynamics of the SARS-CoV-2 Omicron variant.
Despite moderate levels of vaccine effectiveness against symptomatic and severe cases caused by the Omicron variant, especially after booster shots \citep{andres2022omicron}, both vaccine- and infection-derived immunity provided limited protection against infections \citep{pearson2021omicron}.
This immune evasion helped the Omicron variant to cause more infections in South Africa than previous variants \citep{sun2022omicron};
even though the Omicron variant is probably milder than XXX \citep{MENNI20221618,ulloa2022estimates}, the number of hospitalizations and deaths caused by the Omicron variant was high \citep{Iacobuccio254,faust2022omicron,sigal2022estimating}.

There are several limitations to our analysis.
First of all, behavioral and intervention effects must be large in order for the fatality to peak at intermediate levels of asymptomaticity.
While we are able to generalize our results using more realistic models, incorporating both presymptomatic and asymptomatic transmission, the transmission rate needs to be reduced by at least 60\% after symptom onset for us to see the nonlinear effects of subclinical transmission on population-level outcomes.
\swp{what are some other limitations we should address?}
\jd{Something about estimating protection against different endpoints. We should also highlight the importance of doing this estimation.}

SARS-CoV-2 has proven hard to control in large part because transmission is often decoupled from symptoms. 
Although mitigation efforts have often prioritized responding to symptoms---including symptom-based testing, fever checks, mask-wearing for infectious individuals---a different approach that strives to reduce the chance of asymptomatic transmission while increasing treatment of symptomatically infected individuals could both reduce infection risk at the source and in the event that individuals are at risk for severe outcomes.
As more variants continue to emerge, updating vaccines to prevent infections, and not just diseases, will be critical to controlling the course of the pandemic.
\jd{This is complicated. Maybe regular waves of mild SC2 are a good way to control morbidity in the medium term. There is also an argument to make about symptom-focused responses and evolution toward mildness.}
